### 2023-04-07 main.tex
ii

Observe that $g_{c}(\cdot)$ is surjective and bijective, and thus invertible. \\

@@

@@

On the occupation variable $n_{d}^{L}$ the action is similar, but with the upper case $1$ replaced by $L$
 In the spirit of \cite{casini2022uphill} we can write he the Master's equation for the evolution of the average density occupation, obtaining a system of $N-1$ difference-differential equation where the discrete Laplacians of all species are coupled and linear reaction terms are present. Therefore, this model is a generalization to $N$ species and to maximal occupation $\nu$ of the one studied in \cite{casini2022uphill}. This answers the first question of the beginning of this section. 

@@

Recalling that, to have reversibility the reservoirs parameters must fulfil $\rho_{a}^{x}=\rho_{a}$ $\forall x \in V$ and $\forall a\in \{1,\ldots,N\}$, we obtain the result. 

@@

\textbf{Remark}: the generator $\mathcal{L}^{rd}$ has a dual with respect to the same duality function of $\mathcal{L}$ of the multi-species stirring process. Moreover, the dual process has absorbing boundaries while it performs the same edge dynamics of $\mathcal{L}^{rd}$. As we will show this follows from the same $gl(N)$ algebraic structure. 

@@

With this prove we answered to the second and third questions stated at the beginning of this section.

>>>>

Observe that $g_{c}(\cdot)$ is surjective and injective, and thus invertible. \\

@@

\begin{equation}\label{actionBDLine}

@@

On the occupation variable $n_{d}^{L}$ the action is similar, but with the upper case $1$ replaced by $L$.\\ In the spirit of \cite{casini2022uphill} we can define the average density occupation of species $a$ at site $x$ as
 	\rho_{a}(x,t)=\mathbb{E}_{\mu}\left[n_{a}^{x}(t)\right]
 where $\mathbb{E}_{\mu}$ denotes the expectation with respect to the law of the Markov process $(\bm{n})_{t\geq 0}$ initialized with arbitrary initial measure $\mu$. They evolve according to the Master's equation
 	\frac{d \rho_{a}(x,t)}{dt}=\mathbb{E}_{\mu}\left[\mathcal{L}^{rd}n_{a}^{x}(t)\right]
Therefore, using the action of $\mathcal{L}^{rd}$ expressed by \eqref{DifferenceEquation} and \eqref{actionBDLine} we obtaina system of $N-1$ difference-differential equation where the discrete Laplacians of all species are coupled and linear reaction terms are present. For these reasons, this model is a generalization to $N$ species and to maximal occupation $\nu$ of the one studied in \cite{casini2022uphill}. This answers the first question of the beginning of this section. 

@@

Recalling that, to have reversibility, the reservoirs parameters must fulfil $\rho_{a}^{x}=\rho_{a}$ $\forall x \in V$ and $\forall a\in \{1,\ldots,N\}$, we obtain the result. 

@@

\textbf{Remark}: the generator $\mathcal{L}^{rd}$ has a dual $\widetilde{\mathcal{L}}^{rd}$ with respect to the same duality function \eqref{dualityElements} of the multi-species stirring process. The dual process has absorbing boundaries while it performs the same edge dynamics of $\mathcal{L}^{rd}$. As we will show this follows from the same $gl(N)$ algebraic structure. 

@@

With this prove we answered the second and third questions stated at the beginning of this section.
